---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geoSAE

<!-- badges: start -->
<!-- badges: end -->

This function is an extension of the Small Area Estimation (SAE) model. Geoadditive Small Area Model is a combination of the geoadditive model with the Small Area Estimation (SAE) model, by adding geospatial information to the SAE model. 

## Authors

Ketut Karang Pradnyadika, Ika Yuni Wulansari

## Maintainer

Ketut Karang Pradnyadika <221709776@stis.ac.id>

## Installation

You can install the released version of geoSAE from [CRAN](https://CRAN.R-project.org) or find my github repository [Github](https://github.com/ketutdika)

## Example

``` {r}
library(geoSAE)

#Load the dataset for unit level
data(dataUnit)

#Load the dataset for spline-2
data(zspline)

#Load the dataset for area level
data(dataArea)

#Construct the data frame
y       <- dataUnit$y
x1      <- dataUnit$x1
x2      <- dataUnit$x2
x3      <- dataUnit$x3
formula <- y~x1+x2+x3
zspline <- as.matrix(zspline[,1:10])
dom     <- dataUnit$area
xmean   <- cbind(1,dataArea[,2:4])
zmean   <- dataArea[,5:14]
number  <- dataUnit$number
area    <- dataUnit$area
data    <- data.frame(number, area, y, x1, x2, x3)

#Estimate EBLUP
eblup_geosae <- eblupgeo(formula, zspline, dom, xmean, zmean, data)
eblup_geosae$eblup
 
#Estimate MSE
mse_geosae <- pbmsegeo(formula,zspline,dom,xmean,zmean,data,B=100)
mse_geosae$mse
 
## eblup_geosae$eblup        #to see the result of EBLUPs with Geoadditive Small Area Model each area
## mse_geosae$mse            #to see the result of MSE with Geoadditive Small Area Model each area
```

## References

- Rao, J.N.K & Molina. (2015). Small Area Estimation 2nd Edition. New York: John Wiley and Sons, Inc.
- Bocci, C., & Petrucci, A. (2016). Spatial information and geoadditive small area models. Analysis of poverty data by small area estimation, 245-259.
- Ardiansyah, M., Djuraidah, A., & Kurnia, A. (2018). PENDUGAAN AREA KECIL DATA PRODUKTIVITAS TANAMAN PADI DENGAN GEOADDITIVE SMALL AREA MODEL. Jurnal Penelitian Pertanian Tanaman Pangan, 2(2), 101-110. 


